\documentclass{article}

\usepackage{cmbright} 
\usepackage{scalefnt} 
\usepackage{amssymb} 
\usepackage{amsmath} %\usepackage[utf8]{inputenc}
\usepackage{fontspec}

% Bad examples:
% http://math.mit.edu/topology/posters/20140303-Tyler-Lawson.pdf
\include{templates/poster_fitbox}
\fontdim24pt % Maximum abstract font size for fitbox



\DeclareMathOperator{\N}{\mathbb{N}} 
\DeclareMathOperator{\Z}{\mathbb{Z}} 
\DeclareMathOperator{\Q}{\mathbb{Q}} 
\DeclareMathOperator{\R}{\mathbb{R}} 
\DeclareMathOperator{\C}{\mathbb{C}}
\let\H\relax
\DeclareMathOperator{\H}{\mathbb{H}} 
\DeclareMathOperator{\A}{\mathbb{A}}


\def\infinity{\ifmmode \infty\else ∞\fi}
\catcode`\∞=\active
\let∞\infinity


\providecommand{\mparwidth}{1in} 
\providecommand{\mtop}{0.5in} 
\providecommand{\mbottom}{0.5in} 
\providecommand{\mleft}{0.5in} 
\providecommand{\mright}{0.5in} 
\usepackage[top = \mtop, bottom = \mbottom, left = \mleft, right=\mright, marginparwidth=\mparwidth]{geometry} 
\pagenumbering{gobble}

 
\begin{document}

\begin{center}

{\scalefont{5}Topology Seminar} \medskip\vspace{1.2cm}

{\scalefont{3.6}{\bf Gonçalo Tabuada}}\\\vspace{20pt} {\scalefont{2}of Universidade Nova de Lisboa will be speaking on}\\\vspace{30pt} {\scalefont{3.6}
    Non-commutative motives
}\\\vspace{20pt} {\scalefont{2}on March 29 at 4:30 
in \\\vspace{6pt}MIT Room 2-131}\\ 
\end{center}

\vfill

\begin{fitbox}{0.9\textwidth}{11.5cm}
In this talk I will describe the construction of the category of non-commutative motives $[1,2,3]$ in Drinfeld-Kontsevich's non-commutative algebraic geometry program. In the process, I will present the first conceptual characterization of Quillen's higher K-theory since Quillen's foundational work in the 70's. As an application, I will show how these results allow us to obtain for free the higher Chern character from K-theory to cyclic homology.

References:

[1] D.-C. Cisinski and G. Tabuada, Symmetric monoidal structure on
Non-commutative motives. Available at arXiv:1001.0228.

[2] D.-C. Cisinski and G. Tabuada, Non-connective K-theory via universal
invariants. Available at arXiv:0903.3717.

[3] G. Tabuada, Higher K-theory via universal invariants. Duke Math.
Journal, 145 (2008), no.1, 121-206.
2010/03/30,,,,Matthew Gelvin" 
\end{fitbox}

\vfill
\end{document}

% vim:ft=tex 
