\documentclass{article}

\usepackage{cmbright} 
\usepackage{scalefnt} 
\usepackage{amssymb} 
\usepackage{amsmath} %\usepackage[utf8]{inputenc}
\usepackage{fontspec}

% Bad examples:
% http://math.mit.edu/topology/posters/20140303-Tyler-Lawson.pdf
\include{templates/poster_fitbox}
\fontdim24pt % Maximum abstract font size for fitbox



\DeclareMathOperator{\N}{\mathbb{N}} 
\DeclareMathOperator{\Z}{\mathbb{Z}} 
\DeclareMathOperator{\Q}{\mathbb{Q}} 
\DeclareMathOperator{\R}{\mathbb{R}} 
\DeclareMathOperator{\C}{\mathbb{C}}
\let\H\relax
\DeclareMathOperator{\H}{\mathbb{H}} 
\DeclareMathOperator{\A}{\mathbb{A}}


\def\infinity{\ifmmode \infty\else ∞\fi}
\catcode`\∞=\active
\let∞\infinity


\providecommand{\mparwidth}{1in} 
\providecommand{\mtop}{0.5in} 
\providecommand{\mbottom}{0.5in} 
\providecommand{\mleft}{0.5in} 
\providecommand{\mright}{0.5in} 
\usepackage[top = \mtop, bottom = \mbottom, left = \mleft, right=\mright, marginparwidth=\mparwidth]{geometry} 
\pagenumbering{gobble}

 
\begin{document}

\begin{center}

{\scalefont{5}Topology Seminar} \medskip\vspace{1.2cm}

{\scalefont{3.6}{\bf David Ayala}}\\\vspace{20pt} {\scalefont{2}of Harvard University will be speaking on}\\\vspace{30pt} {\scalefont{3.6}
    A combinatorial $E_n$ operad
}\\\vspace{20pt} {\scalefont{2}on November 22 at 4:30 
in \\\vspace{6pt}MIT Room 2-131}\\ 
\end{center}

\vfill

\begin{fitbox}{0.9\textwidth}{11.5cm}
I will propose a simple and combinatorial 
$E_n$-operad which is built out of finite posets indexing a stratification 
of configuration spaces of points in an $n$-disk.  This poset is 
constructed from a category $\theta_n$ which has recently become an 
important player for modeling weak $n$-categories (Joyal, Berger, Rezk).  
The techniques involved use the formalism of quasi-categories (Lurie).  This project is joint with Richard Hepworth (Copenhagen) and is a work in progress.

One (nearly achieved) goal is to directly and geometrically relate three 
well-developed methods for recognizing $n$-fold loop spaces: as certain 
algebras over the little $n$-disk operad, as certain algebras over the 
Barratt-Eccles $E_n$ operad (via the Smith filtration), and as certain 
presheaves on $\theta_n$ (Berger).  A version of Dunn's additivity theorem 
becomes a formal consequence of the setup.  A farther away goal is to 
imitate the construction of topological chiral homology using this proposed $E_n$-operad.  This should have the benefit of making topological chiral homology (and possibly other field theories) more prepared for computations. 
\end{fitbox}

\vfill
\end{document}

% vim:ft=tex 
