\documentclass{article}

\usepackage{cmbright} 
\usepackage{scalefnt} 
\usepackage{amssymb} 
\usepackage{amsmath} %\usepackage[utf8]{inputenc}
\usepackage{fontspec}

% Bad examples:
% http://math.mit.edu/topology/posters/20140303-Tyler-Lawson.pdf
\include{templates/poster_fitbox}
\fontdim24pt % Maximum abstract font size for fitbox



\DeclareMathOperator{\N}{\mathbb{N}} 
\DeclareMathOperator{\Z}{\mathbb{Z}} 
\DeclareMathOperator{\Q}{\mathbb{Q}} 
\DeclareMathOperator{\R}{\mathbb{R}} 
\DeclareMathOperator{\C}{\mathbb{C}}
\let\H\relax
\DeclareMathOperator{\H}{\mathbb{H}} 
\DeclareMathOperator{\A}{\mathbb{A}}


\def\infinity{\ifmmode \infty\else ∞\fi}
\catcode`\∞=\active
\let∞\infinity


\providecommand{\mparwidth}{1in} 
\providecommand{\mtop}{0.5in} 
\providecommand{\mbottom}{0.5in} 
\providecommand{\mleft}{0.5in} 
\providecommand{\mright}{0.5in} 
\usepackage[top = \mtop, bottom = \mbottom, left = \mleft, right=\mright, marginparwidth=\mparwidth]{geometry} 
\pagenumbering{gobble}

 
\begin{document}

\begin{center}

{\scalefont{5}Topology Seminar} \medskip\vspace{1.2cm}

{\scalefont{3.6}{\bf Inna Zakharevich}}\\\vspace{20pt} {\scalefont{2}of University of Chicago will be speaking on}\\\vspace{30pt} {\scalefont{3.6}
    The annihilator of the Lefschetz motive
}\\\vspace{20pt} {\scalefont{2}on March 7 at 4:30 
in \\\vspace{6pt}MIT Room 2-131}\\ 
\end{center}

\vfill

\begin{fitbox}{0.9\textwidth}{11.5cm}
The Grothendieck ring of varieties is defined to be the free abelian group generated by varieties, modulo the relation that for a closed subvariety $Y$ of $X$, $[X] = [Y] + [X \backslash Y]$; the ring structure is defined via the Cartesian product.  For example, if $X$ and $Y$ are piecewise isomorphic, in the sense that there exist stratifications on $X$ and $Y$ with isomorphic strata, then $[X] = [Y]$ in the Grothendieck ring.

There are two important questions about this ring:

1.  What does it mean when two varieties $X$ and $Y$ have equal classes in the Grothendieck ring?  Must $X$ and $Y$ be piecewise isomorphic?

2.  Is the class of the affine line a zero divisor?

Last December Borisov answered both of these questions with a single example, by constructing an element $[X] - [Y]$ in the kernel of multiplication by the affine line; in a beautiful coincidence, it turned out that $X \times \Abb^1$ and $Y \times \Abb^1$ were not piecewise isomorphic.  In this talk we will describe an approach using algebraic K-theory to construct a topological version of the Grothendieck ring of varieties. We shall prove that $\pi_1$ of this space is generated by birational automorphisms of varieties which extend to piecewise automorphisms, which allows us to construct a group that surjects onto the kernel of multiplication by the affine line.  By analyzing this group we will sketch a proof that Borisov's coincidence was not a coincidence at all: any element in the kernel of multiplication by the affine line can be represented as $[X]-[Y]$, where $X \times \Abb^1$ and $Y \times \Abb^1$ are not piecewise isomorphic. 
\end{fitbox}

\vfill
\end{document}

% vim:ft=tex 
