\documentclass{article}

\usepackage{cmbright} 
\usepackage{scalefnt} 
\usepackage{amssymb} 
\usepackage{amsmath} %\usepackage[utf8]{inputenc}
\usepackage{fontspec}

% Bad examples:
% http://math.mit.edu/topology/posters/20140303-Tyler-Lawson.pdf
\include{templates/poster_fitbox}
\fontdim24pt % Maximum abstract font size for fitbox



\DeclareMathOperator{\N}{\mathbb{N}} 
\DeclareMathOperator{\Z}{\mathbb{Z}} 
\DeclareMathOperator{\Q}{\mathbb{Q}} 
\DeclareMathOperator{\R}{\mathbb{R}} 
\DeclareMathOperator{\C}{\mathbb{C}}
\let\H\relax
\DeclareMathOperator{\H}{\mathbb{H}} 
\DeclareMathOperator{\A}{\mathbb{A}}


\def\infinity{\ifmmode \infty\else ∞\fi}
\catcode`\∞=\active
\let∞\infinity


\providecommand{\mparwidth}{1in} 
\providecommand{\mtop}{0.5in} 
\providecommand{\mbottom}{0.5in} 
\providecommand{\mleft}{0.5in} 
\providecommand{\mright}{0.5in} 
\usepackage[top = \mtop, bottom = \mbottom, left = \mleft, right=\mright, marginparwidth=\mparwidth]{geometry} 
\pagenumbering{gobble}

\def\TQFT{\mathop{\mathrm{TQFT}}}\def\obj{\mathop{\mathrm{obj}}} 
\begin{document}

\begin{center}

{\scalefont{5}Topology Seminar} \medskip\vspace{1.2cm}

{\scalefont{3.6}{\bf John Francis}}\\\vspace{20pt} {\scalefont{2}of Northwestern University will be speaking on}\\\vspace{30pt} {\scalefont{3.6}
    Factorization homology and the cobordism hypothesis
}\\\vspace{20pt} {\scalefont{2}on May 15 at 4:30 
in \\\vspace{6pt}MIT Room 2-131}\\ 
\end{center}

\vfill

\begin{fitbox}{0.9\textwidth}{11.5cm}
The cobordism hypothesis—after Baez–Dolan, Costello, Hopkins–Lurie, and Lurie—asserts that for a
symmetric monoidal $(\infty,n)$-category $C$ in which every object has a dual and every $k$-morphism has a left and
right adjoint for $k<n$, there is an equivalence $\TQFT(C) = \obj(C)$ between $C$-valued framed topological field theories
and objects of $C$. This is the formulation due to Lurie. I'll give a proof of the cobordism hypothesis based on
factorization homology. Factorization homology is a multiplicative analogue of ordinary homology. Usual homology
integrates an abelian group, chain complex, or spectrum over a manifold $M$, which one can think as the moduli space
of points in $M$ itself. The result takes disjoint unions of manifolds to direct sums. The alpha version of
factorization homology integrates an $E_n$-algebra over a moduli space of finite subsets of a manifold $M$. The beta
version of factorization homology integrates an $(\infty, n)$-category over the moduli space of stratifications of
$M$. The result takes disjoint unions to tensor products. I'll define this beta version of factorization homology.
It satisfies a version of the Eilenberg–Steenrod axioms—this part is work in progress. These Eilenberg–Steenrod
axioms together with an argument in the spirit of Pontryagin–Thom theory implies the cobordism hypothesis. This
is joint work with David Ayala. 
\end{fitbox}

\vfill
\centerline{\scalefont{1.2} For information, write: \texttt{lpanchev@mit.edu} } 
\vfill 
\end{document}

% vim:ft=tex 
